Results

### 2024-09-16 scripts/Results.Rmd
props

```{r}
ggplot () + 
  geom_bar(data = files, aes(Rank))

@@

need_patches <- unique(files$f_rankedp)
patch_summs <- lapply(need_patches, PatchSummary)

@@

- can we test moving the distance patches into their own categories ??? 
```{r}
hist(fp$Rank)
```

>>>>

```{r, eval = F}

@@

need_patches <- unique(files$f_rankedp) 
patch_summs <- lapply(need_patches, PatchSummary)|> 
  bind_rows()

ggplot() + 
  geom_point(data = patch_summs, aes(x = Rank, y = Area_ha))

ggplot() + 
  geom_point(data = patch_summs, aes(x = Rank, y = Patches))

ps <- patch_summs |>
  ungroup() |>
  group_by(Rank) |>
  summarize(
    meanP = mean(Patches),
    meanA = mean(Area_ha)
    )

f1 <- files |>
  sf::st_drop_geometry() |>
  count(Rank) |>
  drop_na() |>
  left_join(ps, 'Rank') |>
  mutate(
    meanP_prop = (1 - meanP) * n,
    meanA_prop = (1 - meanA) * n
  )

ggplot () + 
  geom_col(data = f1, aes(meanP_prop, x = Rank))

ggplot () + 
  geom_col(data = f1, aes(meanA_prop, x = Rank))

saveRDS(patch_summs, file = '../data/processed/PatchCtsAreas.rds')
```

@@

```{r}
hist(fp$Rank)
```
